method-qc

### 2017-09-18 analysis/method-qc.Rmd

```{r}
ggplot(rules_info,aes(log(Citations+1),`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name))

cit_breaks <- c(0, 1, 10, 100, max(rules_info$Citations))
ggplot(rules_info,aes(Citations+1,`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name)) +
  scale_x_log10(breaks = cit_breaks+1, labels = cit_breaks)

@@

ggplot(rules_info,aes(date,`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name)) +
  scale_y_continuous(breaks = seq_len(10))

@@

```{r}

>>>>

```{r}
ggplot(rules_info,aes(log(Citations+1), qc_score))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name))

cit_breaks <- c(0, 1, 10, 100, max(rules_info$Citations))
ggplot(rules_info,aes(Citations+1, qc_score))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name)) +
  scale_x_log10(breaks = cit_breaks+1, labels = cit_breaks)

@@

ggplot(rules_info,aes(date, qc_score)) +
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name)) +
  scale_y_continuous(breaks = seq_len(10))

@@

Different methods generate different kinds of output...
```{r}
rules_info %>% filter(wrapper == "Done") %>% select(ids, output) %>% 
  separate_rows(ids, sep=",") %>% 
  separate_rows(output, sep=",") %>% 
  mutate(output=trimws(output)) %>% 
  ggplot() + 
    geom_bar(aes(output)) +
    coord_flip()
```
